Type cones of $\b{g}$-vector fans

### 2019-04-01 thirdPaper/draft/typeConeAssociahedra.tex
improvements Sec 2

% Graph associahedra
\newcommand{\ground}{V} % ground set
\newcommandx{\graphG}[1][1=G]{#1} % graph
\newcommandx{\tube}[1][1=t]{\mathsf{#1}} % tube
\newcommandx{\tubes}{\mathcal{T}} % all tubes
\newcommandx{\tubing}[1][1=T]{\mathsf{#1}} % tubing
\newcommand{\connectedComponents}{\kappa} % connected components
\newcommand{\nestedComplex}{\mathcal{N}} % nested complex
\newcommand{\nonDisconnecting}{\mathrm{nd}} % non-disconnecting vertices
\newcommand{\neighbors}{\mathrm{ne}} % neighbors

@@

\subsubsection{Type cone of $\b{g}$-vector fans}

@@

@@

\begin{definition}[{\cite[Def.~{4.8}]{PaluPilaudPlamondon-nonkissing}}]
The \defn{$\b{g}$-vector} of a walk~$\omega$ is~$\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}$.
We denote by~$\gvectors{F} \eqdef \set{\gvector{\omega}}{\omega \in F}$ the set of $\b{g}$-vectors of a facet~$F$.
\end{definition}

@@

\begin{definition}[{\cite[Def.~{4.11}]{PaluPilaudPlamondon-nonkissing}}]
The \defn{$\b{c}$-vector} of a walk~$\omega$ in a non-kissing facet~${F \in \NKC}$ is~${\cvector{F}{\omega} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}}}$, where~$\distinguishedSign{\omega}{F} \in \{-1,1\}$ is positive if~${\distinguishedString{\omega}{F} \in \Sigma_\top(\omega)}$ and negative if~${\distinguishedString{\omega}{F} \in \Sigma_\bottom(\omega)}$.
We denote by~$\cvectors{F} \eqdef \set{\cvector{F}{\omega}}{\omega \in F}$ the set of $\b{c}$-vectors~of~a~facet~$F$.
\end{definition}

@@

\smallskip
\item \textbf{Dissection quivers}: Consider a dissection~$D$ of a convex polygon~$P$ (that is a crossing-free set of diagonals of~$P$) and its \defn{gentle dissection quiver}~$\quiver_D$, whose vertices are the internal diagonals of~$D$, whose arrows connect pairs of consecutive internal diagonals along the boundary of a face of~$D$, and whose relations correspond to triples of consecutive internal diagonals along the boundary of a face of~$D$. The non-kissing complex of~$\quiver_D$ the corresponds to non-crossing sets of accordions of~$D$, where an accordion is a segment connecting the middles of two boundary edges of~$P$ and crossing a connected set of diagonals of~$D$. This accordion complex was studied in~\cite{GarverMcConville} and~\cite{MannevillePilaud-accordion} with motivation coming from~\cite{Baryshnikov}, and~\cite{Chapoton-quadrangulations}.
\end{enumerate}

@@

\begin{example}
\label{exm:typeConeNKC}
Consider the gentle quivers of \cref{fig:typeConeNKC}.
\vincent{Todo}
\end{example}

@@

In this section, we focus on the following family of gentle quivers, which was also considered in~\cite[Sect.~4]{GarverMcConvilleMousavand}.

@@

We say that a gentle quiver~$\quiver$ is \defn{simple} when
\begin{itemize}
\item it satisfies the three equivalent conditions of \cref{prop:noSelfKissing},
\item it contains no cycle of length~$2$.
\end{itemize}
Note that this family already contains a lot of relevant examples, including the grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
In particular, the classical associahedron is the gentle associahedron of a simple gentle quiver.
We will see in~\cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a simple gentle quiver~$\quiver$ happens to be simplicial, and we will derive in~\cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.

@@

\para{Nested complex}
%
Let~$\graphG$ be a graph with vertex set~$\ground$.
Let~$\connectedComponents(\graphG)$ denote the set of connected components of~$\graphG$ and define~$n \eqdef |\ground|-|\connectedComponents(\graphG)|$.
A \defn{tube} of~$\graphG$ is a connected induced subgraph of~$\graphG$.
The set of tubes of~$\graphG$ is denoted by~$\tubes(\graphG)$.
The inclusion maximal tubes of~$\graphG$ are its connected components~$\connectedComponents(\graphG)$.
The tubes which are neither empty nor maximal are called \defn{proper}.
Two tubes~$\tube, \tube'$ of~$\graphG$ are \defn{compatible} if they are either nested (\ie $\tube \subseteq \tube'$ or~$\tube' \subseteq \tube$), or disjoint and non-adjacent (\ie $\tube \cup \tube'$ is not a tube of~$\graphG$).
A \defn{tubing} on~$\graphG$ is a set~$\tubing$ of pairwise compatible proper tubes of~$\graphG$.
The \defn{nested complex} of~$\graphG$ is the simplicial complex~$\nestedComplex(\graphG)$ of all tubings on~$\graphG$.

\para{Nested fan and graph associahedron}
%
Let~$(\b{e}_v)_{v \in \ground}$ be the canonical basis of~$\R^\ground$.
We consider the hyperplane~${\HH \eqdef \bigset{\b{x} \in \R^\ground}{\sum_{w \in W} x_w = 0 \text{ for all } W \in \connectedComponents(\graphG)}}$ and let~$\pi : \R^\ground \to \HH$ denote the orthogonal projection on~$\HH$.
The \defn{$\b{g}$-vector} of a tube~$\tube$ of~$\graphG$ is the projection~$\gvector{\tube} \eqdef \pi \big( \sum_{v \in \tube} \b{e}_v \big)$ of the characteristic vector of~$\tube$.
Note that by definition,~$\gvector{\graphG} = 0$.
We also define~$\gvectors{\tubing} \eqdef \set{\gvector{\tube}}{\tube \in \tubing}$ for a tubing~$\tubing$ on~$\graphG$.
These vectors support a complete simplicial fan realization of the nested complex.
Examples are illustrated in \cref{fig:nestedFans}.

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.55]{nestedFans}}
	\caption{Two nested fans. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$.}
	\label{fig:nestedFans}
\end{figure}

\begin{theorem}[\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
For any graph~$\graphG$, the set of cones
\[
\gvectorFan[\graphG] \eqdef \set{\R_{\ge 0} \, \gvectors{\tubing}}{\tubing \text{ tubing on } \graphG}
\]
is a complete simplicial fan of~$\HH$, called \defn{nested fan} of~$\graphG$, which realizes the nested complex~$\nestedComplex(\graphG)$.
\end{theorem}

@@

\begin{theorem}[\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
For any graph~$\graphG$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron~$\Asso[\graphG]$, defined as the Minkowski sum~$\sum_{\tube \in \tubes(\graphG)} \triangle_{\tube}$ of the faces of the standard simplex corresponding to all tubes of~$\graphG$.
\end{theorem}

@@

We are now ready to describe the type cone of the nested fan~$\gvectorFan[\graphG]$.
We first treat the case when~$G$ is a path so that the $\graphG$-associahedron is a classical associahedron.
We show that the type cone is then simplicial which gives another proof of \cref{thm:simplicialTypeConeAsso} and \cref{coro:descriptionAllAsso}.

\subsubsection{Simplicial type cones for path associahedra}

We start with the case of the path on~$n+1$ vertices.
Recall that the tubes of the path are the intervals of~$[n+1]$ and that two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ are exchangeable if either~${i < i' \le j+1 < j'+1}$ or~${i' < i \le j'+1 < j+1}$.

@@

\begin{proof}
Let~$(\b{f}_{[i,j]})_{1 \le i \le j \le n}$ be the canonical basis of~$\R^{\binom{n+1}{2}}$.
Consider two exchangeable tubes~$[i,j]$ and~$[i',j']$ with~${i < i' \le j+1 < j'+1}$.
By \cref{prop:exchangeablePairsGA}\,(iii), the linear dependence between the corresponding $\b{g}$-vectors is given by
\[
\gvector{[i,j]} + \gvector{[i',j']} = \gvector{[i,j']} + \gvector{[i',j]}.
\]
Therefore, the outer normal vector of the corresponding inequality of the type cone~$\typeCone(\gvectorFan[\graphG])$ is
\[
\b{n}(i,j,i',j') \eqdef \b{f}_{[i,j]} + \b{f}_{[i',j']} - \b{f}_{[i,j']} - \b{f}_{[i',j]}.
\]
Denoting
\[
\b{m}(k,\ell) \eqdef \b{n}(k,\ell-1,k+1,\ell) = \b{f}_{[k, \ell-1]} + \b{f}_{[k+1, \ell]} - \b{f}_{[k, \ell]} - \b{f}_{[k+1, \ell-1]},
\]
we obtain that
\[
\b{n}(i,j,i',j') = \sum_{\substack{k \in {[i,i'[} \\ \ell \in {]j,j']}}} \b{m}(k,\ell).
\]
Indeed, on the right hand side, the basis vector~$\b{f}_{[k,\ell]}$ appears with a positive sign in~$\b{m}(k,{\ell+1})$ for~$(k,\ell) \in {[i,i'[} \times {[j,j'[}$ and in~$\b{m}(k-1, \ell)$ for~$(k,\ell) \in {]i,i']} \times {]j,j']}$, and with a negative sign in~$\b{m}(k,\ell)$ for~$(k,\ell) \in {[i,i'[} \times {]j,j']}$ and in~$\b{m}(k-1,\ell+1)$ for~$(k,\ell) \in {]i,i']} \times {[j,j'[}$.
Therefore, these contributions all vanish except when~$[k, \ell]$ is one of the tubes~$[i,j]$, $[i',j']$, $[i,j']$ or~$[i',j]$.
%For any~$i \le k < i'$ and~$j < \ell \le j'$, the exchange relation between the tubes~$[k, \ell-1]$ and~$[k+1, \ell]$ is given by
%\begin{equation}
%\label{eq:exch2}
%\tag{$\mathrm{ER}_k^\ell$}
%\gvector{[k, \ell-1]} + \gvector{[k+1, \ell]} = \gvector{[k, \ell]} + \gvector{[k+1, \ell-1]}.
%\end{equation}
%Summing the exchange relations~\eqref{eq:exch2} over all pairs~$(k,\ell) \in {[i,i'[} \times {]j,j']}$, we obtain after simplifications the exchange relation~\eqref{eq:exch1}.
%Indeed, the $\b{g}$-vector of each tube~$[k, \ell]$ appears on the left hand sides of the exchange relations~($\mathrm{ER}_k^{\ell+1}$) for~$(k,\ell) \in {[i,i'[} \times {[j,j'[}$ and ($\mathrm{ER}_{k-1}^\ell$) for~$(k,\ell) \in {]i,i']} \times {]j,j']}$ and on the right hand sides of the exchange relations~($\mathrm{ER}_k^\ell$) for~$(k,\ell) \in {[i,i'[} \times {]j,j']}$ and~($\mathrm{ER}_{k-1}^{\ell+1}$) for~$(k,\ell) \in {]i,i']} \times {[j,j'[}$.
%Therefore, these contributions all vanish except when~$[k, \ell]$ is one of the tubes~$[i,j]$, $[i',j']$, $[i,j']$ or~$[i',j]$.
This shows that any exchange relation is a positive linear combination of the exchange relations corresponding to all pairs of tubes~$[i,j]$ and~$[i',j']$ of~$[n+1]$ such that~$i = i'+1$ and~$j = j'+1$.

We now need to show that all these exchangeable pairs are extremal.
Assume that~$\b{m}(k,\ell)$ can be written as the linear combination
\begin{equation}
\label{eq:linComb}
\b{m}(k,\ell) = \sum \lambda(i,j,i',j') \, \b{n}(i,j,i',j'),
\end{equation}
where~$\lambda(i,j,i',j') \ge 0$ for all exchangeable pairs~$\{[i,j], [i',j']\}$.
Note that~$\sum \lambda(i,j,i',j') \ge 1$ since the coefficient of~$\b{f}_{[k,\ell]}$ in~$\b{m}(k,\ell)$ is~$-1$.
Consider the linear form~$\Phi: \R^N \to \R$ defined by~$\Phi(\b{f}_{[i,j]}) = -(j-i)^2$.
A quick computation shows that
\[
\Phi(\b{n}(i,j,i',j')) = 2(i'-i)(j'-j).
\]
Applying~$\Phi$ to \cref{eq:linComb}, we obtain
\[
1 = \sum \lambda(i,j,i',j')(i'-i)(j'-j).
\]
Since~$\sum \lambda(i,j,i',j') \ge 1$ we obtain that~$\lambda(k,\ell-1,k+1,\ell) = 1$ and~$\lambda(i,j,i',j') = 0$ for all other exchangeable pairs~$\{[i,j], [i',j']\}$.
\end{proof}

\subsubsection{General case}

@@

\begin{corollary}
\label{coro:extremalExchangeablePairsGA}
The extremal exchangeable pairs for the nested fan of~$\graphG$ are equivalently
\begin{enumerate}[(i)]
\item the pairs of tubes~$\tube[r] \cup \{v\}$ and~$\tube[r] \cup \{v'\}$ for any tube~$\tube[r] \in \tubes(\graphG)$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
\item the pairs of tubes~$\tube[s] \ssm \{v'\}$ and~$\tube[s] \ssm \{v\}$ for any tube~$\tube[s] \in \tubes(\graphG)$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$,
\end{enumerate}
\end{corollary}

@@

%\begin{corollary}
%Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes(\graphG)$ and a height vector~$\b{h} \in \R^{\tubes(\graphG)}$ such that~$\b{h}_{\graphG} = 0$ and
%\[
%\b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]}
%\]
%for any pair of tubes~$\{\tube, \tube'\}$ of~$\graphG$ with~$\tube \ssm \{v\} = \tube' \ssm \{v'\}$ where~$v$ is a neighbor of~$\tube'$ and~$v'$ is a neighbor of~$\tube$.
%Then the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
%\[
%\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes(\graphG)}.
%\]
%\end{corollary}

>>>>

% Graph associahedra
\newcommand{\ground}{V} % ground set
\newcommandx{\graphG}[1][1=G]{#1} % graph
\newcommandx{\tube}[1][1=t]{\mathsf{#1}} % tube
\newcommandx{\tubes}[1][1=\graphG]{\mathcal{T}(#1)} % all tubes
\newcommandx{\tubing}[1][1=T]{\mathsf{#1}} % tubing
\newcommand{\connectedComponents}{\kappa} % connected components
\newcommand{\nestedComplex}{\mathcal{N}} % nested complex
\newcommand{\nonDisconnecting}{\mathrm{nd}} % non-disconnecting vertices
\newcommand{\neighbors}{\mathrm{ne}} % neighbors

@@

\subsubsection{Type cone of finite type $\b{g}$-vector fans}

@@

\begin{example}
%sage: B = Matrix([[0,-1,1],[1,0,-1],[-1,1,0]])
%sage: CA = ClusterAlgebra(B)
%
%sage: CA.explore_to_depth(infinity)
%sage: gvectors = CA.cluster_fan().rays()
%sage: for gvector in gvectors:
%....:     print gvector, CA.cluster_variable(gvector)
%....:     
%N(1, 0, 0) x0
%N(0, 0, 1) x2
%N(1, -1, 0) (x0 + x2)/x1
%N(0, 0, -1) (x0 + x1 + x2)/(x1*x2)
%N(-1, 0, 1) (x1 + x2)/x0
%N(0, -1, 0) (x0 + x1 + x2)/(x0*x1)
%N(-1, 0, 0) (x0 + x1 + x2)/(x0*x2)
%N(0, 1, 0) x1
%N(0, 1, -1) (x0 + x1)/x2
%
%sage: TCCA = type_cone_CA(CA)
%sage: TCCA
%A 9-dimensional polyhedron in QQ^9 defined as the convex hull of 1 vertex, 6 rays, 3 lines
%sage: TCCA.inequalities()
%(An inequality (-1, 0, 1, -1, 0, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (1, 0, -1, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, -1, 1, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 1, 0, 0, -1, 0, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 1, 0, 0, 0, 1, -1) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 1, 0, -1, -1, 1) x + 0 >= 0)

%sage: B = Matrix([[0,-1,2],[1,0,-2],[-1,1,0]])
%sage: CA = ClusterAlgebra(B)
%
%sage: CA.explore_to_depth(infinity)
%sage: gvectors = CA.cluster_fan().rays()
%sage: for gvector in gvectors:
%....:     print gvector, CA.cluster_variable(gvector)
%....:     
%N(-1, 1, 0) (x0^2 + x1^2 + x1*x2)/(x0*x2)
%N(0, 2, -1) (x0^2 + x1^2)/x2
%N(1, 0, 0) x0
%N(0, 0, 1) x2
%N(-2, 0, 1) (x0^2 + x1^2 + 2*x1*x2 + x2^2)/(x0^2*x2)
%N(1, -1, 0) (x0 + x2)/x1
%N(0, 0, -1) (x0^2 + x1^2 + 2*x0*x2 + x2^2)/(x1^2*x2)
%N(-1, 0, 1) (x1 + x2)/x0
%N(0, -1, 0) (x0 + x1 + x2)/(x0*x1)
%N(-1, 0, 0) (x0^2 + x1^2 + x0*x2 + x1*x2)/(x0*x1*x2)
%N(0, 1, 0) x1
%N(0, 1, -1) (x0^2 + x1^2 + x0*x2)/(x1*x2)
%
%sage: TCCA = type_cone_CA(CA)
%sage: TCCA
%A 12-dimensional polyhedron in QQ^12 defined as the convex hull of 1 vertex, 9 rays, 3 lines
%sage: TCCA.lines()
%(A line in the direction (0, 0, 1, 2, 0, 0, -2, 1, -1, -1, 1, -1),
% A line in the direction (1, 2, 0, 0, 0, -1, 0, 0, -1, 0, 1, 1),
% A line in the direction (0, 1, 0, -1, -1, 0, 1, -1, 0, 0, 0, 1))
%sage: TCCA.inequalities()
%(An inequality (-2, 1, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (-1, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 0) x + 0 >= 0,
% An inequality (1, 0, 0, 0, -1, 0, 0, 1, 0, 0, -1, 0) x + 0 >= 0,
% An inequality (0, 0, -1, 0, 0, 1, -1, 0, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (1, -1, 0, 0, 0, 0, 0, 0, 0, -1, 0, 1) x + 0 >= 0,
% An inequality (0, 0, 0, -1, 0, 1, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, 0, 1, 0, 0, 0, 0, -2) x + 0 >= 0,
% An inequality (0, 0, 1, 0, 0, -1, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 1, 1, 0, 0, -2, 0, 0, 0, 0) x + 0 >= 0)
\vincent{todo}
\end{example}

@@

\begin{definition}[{\cite[Def.~{4.8}]{PaluPilaudPlamondon-nonkissing}}]
The \defn{$\b{g}$-vector} of a walk~$\omega$ is~$\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}$.
We set~$\gvectors{F} \eqdef \set{\gvector{\omega}}{\omega \in F}$ for a non-kissing facet~$F \in \NKC$.
\end{definition}

@@

\begin{definition}[{\cite[Def.~{4.11}]{PaluPilaudPlamondon-nonkissing}}]
The \defn{$\b{c}$-vector} of a walk~$\omega$ in a non-kissing facet~${F \in \NKC}$ is~${\cvector{F}{\omega} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}}}$, where~$\distinguishedSign{\omega}{F} \in \{-1,1\}$ is positive if~${\distinguishedString{\omega}{F} \in \Sigma_\top(\omega)}$ and negative if~${\distinguishedString{\omega}{F} \in \Sigma_\bottom(\omega)}$.
We set~$\cvectors{F} \eqdef \set{\cvector{F}{\omega}}{\omega \in F}$ for a non-kissing facet~$F \in \NKC$.
\end{definition}

@@

\smallskip
\item \textbf{Dissection quivers}: Consider a dissection~$D$ of a convex polygon~$P$ (that is a crossing-free set of diagonals of~$P$) and its \defn{gentle dissection quiver}~$\quiver_D$, whose vertices are the internal diagonals of~$D$, whose arrows connect pairs of consecutive internal diagonals along the boundary of a face of~$D$, and whose relations correspond to triples of consecutive internal diagonals along the boundary of a face of~$D$. The non-kissing complex of~$\quiver_D$ then corresponds to non-crossing sets of accordions of~$D$, where an accordion is a segment connecting the middles of two boundary edges of~$P$ and crossing a connected set of diagonals of~$D$. This accordion complex was studied in~\cite{GarverMcConville} and~\cite{MannevillePilaud-accordion} with motivation coming from~\cite{Baryshnikov}, and~\cite{Chapoton-quadrangulations}.
\end{enumerate}

@@

\begin{example}
\label{exm:typeConeNKC}
Consider the gentle quivers of \cref{fig:nonkissingFans}.
%sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}}, [('a','b')])
%
%sage: Q.non_kissing_fan().rays()
%N( 1,  0,  0),
%N( 0,  0,  1),
%N( 1, -1,  0),
%N( 0,  0, -1),
%N( 0, -1,  0),
%N(-1,  0,  0),
%N( 0,  1,  0),
%N( 0,  1, -1)
%in 3-d lattice N
%
%sage: TCNKC = type_cone_NKC(Q)
%sage: TCNKC
%A 8-dimensional polyhedron in QQ^8 defined as the convex hull of 1 vertex, 5 rays, 3 lines
%sage: TCNKC.inequalities()
%(An inequality (-1, 0, 1, -1, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (1, 0, -1, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, 0, -1, 1) x + 0 >= 0,
% An inequality (0, 0, 1, 0, -1, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 1, 0, 0, 1, -1) x + 0 >= 0)
%sage: TCNKC.lines()
%(A line in the direction (0, 0, 1, 0, 1, 0, -1, -1),
% A line in the direction (1, 0, 0, 0, -1, -1, 1, 1),
% A line in the direction (0, 1, 0, -1, 0, 0, 0, -1))

%sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}, 'e3':{'e1':['c']}}, [('b','c')])
%
%sage: Q.non_kissing_fan().rays()
%N( 1,  0,  0),
%N( 0,  0,  1),
%N( 1,  0, -1),
%N( 1, -1,  0),
%N( 0,  0, -1),
%N(-1,  0,  1),
%N( 0, -1,  0),
%N( 0, -1,  1),
%N(-1,  0,  0),
%N( 0,  1,  0),
%N( 0,  1, -1)
%in 3-d lattice N
%
%sage: TCNKC = type_cone_NKC(Q)
%sage: TCNKC
%A 11-dimensional polyhedron in QQ^11 defined as the convex hull of 1 vertex, 9 rays, 3 lines
%sage: TCNKC.inequalities()
%(An inequality (0, 0, 0, 1, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (-1, 0, 1, 0, 0, 0, 0, 0, 0, 1, -1) x + 0 >= 0,
% An inequality (1, 0, -1, 0, 1, 0, 0, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (1, -1, 0, -1, 0, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 0, -1, -1, 1, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 1, -1, -1, 0, 1, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 0, 1, 0, 0, -1, -1, 1) x + 0 >= 0)
%sage: TCNKC.lines()
%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
\vincent{Todo}
\end{example}

@@

The following family of gentle quivers was considered in~\cite[Sect.~4]{GarverMcConvilleMousavand}.

@@

In this section, we need to restrict even further the family of gentle quivers we consider.

\begin{definition}
We say that a gentle quiver~$\quiver$ is \defn{simple} when
\begin{itemize}
\item it satisfies the three equivalent conditions of \cref{prop:noSelfKissing},
\item it contains no cycle of length~$2$.
\end{itemize}
\end{definition}

Note that this family already contains a lot of relevant examples, including the grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
In particular, the classical associahedron is the gentle associahedron of a simple gentle quiver.
We will see in~\cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a simple gentle quiver~$\quiver$ happens to be simplicial, and we will derive in~\cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.

@@

\para{Nested complex}
%
Let~$\graphG$ be a graph with vertex set~$\ground$.
Let~$\connectedComponents(\graphG)$ denote the set of connected components of~$\graphG$ and define~$n \eqdef |\ground|-|\connectedComponents(\graphG)|$.
A \defn{tube} of~$\graphG$ is a connected induced subgraph of~$\graphG$.
The set of tubes of~$\graphG$ is denoted by~$\tubes$.
The inclusion maximal tubes of~$\graphG$ are its connected components~$\connectedComponents(\graphG)$.
The tubes which are neither empty nor maximal are called \defn{proper}.
Two tubes~$\tube, \tube'$ of~$\graphG$ are \defn{compatible} if they are either nested (\ie $\tube \subseteq \tube'$ or~$\tube' \subseteq \tube$), or disjoint and non-adjacent (\ie $\tube \cup \tube'$ is not a tube of~$\graphG$).
A \defn{tubing} on~$\graphG$ is a set~$\tubing$ of pairwise compatible proper tubes of~$\graphG$.
The \defn{nested complex} of~$\graphG$ is the simplicial complex~$\nestedComplex(\graphG)$ of all tubings on~$\graphG$.

\para{Nested fan and graph associahedron}
%
Let~$(\b{e}_v)_{v \in \ground}$ be the canonical basis of~$\R^\ground$.
We consider the hyperplane~${\HH \eqdef \bigset{\b{x} \in \R^\ground}{\sum_{w \in W} x_w = 0 \text{ for all } W \in \connectedComponents(\graphG)}}$ and let~$\pi : \R^\ground \to \HH$ denote the orthogonal projection on~$\HH$.

\begin{definition}
The \defn{$\b{g}$-vector} of a tube~$\tube$ of~$\graphG$ is the projection~$\gvector{\tube} \eqdef \pi \big( \sum_{v \in \tube} \b{e}_v \big)$ of the characteristic vector of~$\tube$.
We set~$\gvectors{\tubing} \eqdef \set{\gvector{\tube}}{\tube \in \tubing}$ for a tubing~$\tubing$ on~$\graphG$.
\end{definition}

Note that by definition, $\gvector(\varnothing) = 0$ and $\gvector{W} = 0$ for all connected components~$W \in \connectedComponents(\graphG)$.
These vectors support a complete simplicial fan realization of the nested complex.
Examples are illustrated in \cref{fig:nestedFans}.

\begin{figure}[b]
	\capstart
	\centerline{\includegraphics[scale=.55]{nestedFans}}
	\caption{Two nested fans. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$.}
	\label{fig:nestedFans}
\end{figure}

\begin{theorem}[\cite{CarrDevadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
\label{thm:nestedFan}
For any graph~$\graphG$, the set of cones
\[
\gvectorFan[\graphG] \eqdef \set{\R_{\ge 0} \, \gvectors{\tubing}}{\tubing \text{ tubing on } \graphG}
\]
is a complete simplicial fan of~$\HH$, called \defn{nested fan} of~$\graphG$, which realizes the nested complex~$\nestedComplex(\graphG)$.
\end{theorem}

@@

\begin{theorem}[\cite{CarrDevadoss, Devadoss, Postnikov, FeichtnerSturmfels, Zelevinsky}]
For any graph~$\graphG$, the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron~$\Asso[\graphG]$, defined as the Minkowski sum~$\sum_{\tube \in \tubes} \triangle_{\tube}$ of the faces of the standard simplex corresponding to all tubes of~$\graphG$.
\end{theorem}

@@

\subsubsection{Type cones of graphical nested fans}

We now discuss the type cones of the graphical nested fans defined in \cref{thm:nestedFan}.
We first obtain from \cref{prop:exchangeablePairsGA} the following redundant description.

\begin{corollary}
For any graph~$\graphG$, the type cone of the nested fan~$\gvectorFan[\graphG]$ is given by
\[
\typeCone(\gvectorFan[\graphG]) = \set{\b{h} \in \R^{\tubes}}{\begin{array}{l} \b{h}_{\tube} = 0 \text{ for any improper tube } \tube \\ \b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]} \text{ for any exchangeable tubes } \tube, \tube' \end{array}}.
\]
\end{corollary}

\begin{example}
\label{exm:typeConeGA}
\vincent{Todo}
\end{example}

In the remaining of this section, we describe the facet defining inequalities of the type cone of the graphical nested fans.
Observe first that we have already indirectly described this type cone when the graph is a path in \cref{prop:extremalExchangeablePairsAsso}.
Recall that on the path with~$n+1$ vertices, the tubes of the path are the intervals of~$[n+1]$ and that two intervals~$[i,j]$ and~$[i',j']$ of~$[n+1]$ are exchangeable if either~${i < i' \le j+1 < j'+1}$ or~${i' < i \le j'+1 < j+1}$.

@@

@@

\begin{corollary}
\label{coro:extremalExchangeablePairsGA}
The extremal exchangeable pairs for the nested fan of~$\graphG$ are equivalently
\begin{enumerate}[(i)]
\item the pairs of tubes~$\tube[r] \cup \{v\}$ and~$\tube[r] \cup \{v'\}$ for any tube~$\tube[r] \in \tubes$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
\item the pairs of tubes~$\tube[s] \ssm \{v'\}$ and~$\tube[s] \ssm \{v\}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$,
\end{enumerate}
\end{corollary}

@@

%\begin{corollary}
%Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$ and a height vector~$\b{h} \in \R^{\tubes}$ such that~$\b{h}_{\graphG} = 0$ and
%\[
%\b{h}_{\tube} + \b{h}_{\tube'} > \b{h}_{\tube \cup \tube'} + \sum_{\tube[s] \in \connectedComponents(\tube \cap \tube')} \b{h}_{\tube[s]}
%\]
%for any pair of tubes~$\{\tube, \tube'\}$ of~$\graphG$ with~$\tube \ssm \{v\} = \tube' \ssm \{v'\}$ where~$v$ is a neighbor of~$\tube'$ and~$v'$ is a neighbor of~$\tube$.
%Then the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
%\[
%\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}.
%\]
%\end{corollary}

\begin{corollary}
Consider a graph~$\graphG$ on~$\ground$ with tubes~$\tubes$ and a height vector~$\b{h} \in \R^{\tubes}$ such that~$\b{h}_{\varnothing} = \b{h}_{\graphG} = 0$ and satisfying one of the two following equivalent conditions:
\begin{enumerate}[(i)]
\item $\b{h}_{\tube[r] \cup \{v\}} + \b{h}_{\tube[r] \cup \{v'\}} > \b{h}_{\tube[r] \cup \{v, v'\}} + \b{h}_{\tube[r]}$ for any tube~$\tube[r] \in \tubes$ and distinct neighbors~$v,v'$ of~$\tube[r]$,
\item $\b{h}_{\tube[s] \ssm \{v'\}} + \b{h}_{\tube[s] \ssm \{v\}} > \b{h}_{\tube[s]} + \b{h}_{\tube[s] \ssm \{v, v'\}}$ for any tube~$\tube[s] \in \tubes$ and distinct non-disconnecting vertices~$v,v'$ of~$\tube[s]$.
\end{enumerate}
Then the nested fan~$\gvectorFan[\graphG]$ is the normal fan of the graph associahedron
\[
\set{\b{x} \in \R^\ground}{\dotprod{\gvector{\tube}}{\b{x}} \le \b{h}_{\tube} \text{ for any tube } \tube \in \tubes}.
\]
\end{corollary}
